%-------------------------
% Resume in Latex
% Author : Aras Gungore
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{hyphenat}
\usepackage{fontawesome}

\usepackage{xcolor}
% Define your custom colors
\definecolor{light_blue}{HTML}{328998}
\definecolor{light_gray}{HTML}{434E5E}
\definecolor{dark_blue}{HTML}{3582C4}
\definecolor{green}{HTML}{22A162}
\definecolor{purple}{HTML}{59578E}
\definecolor{pink}{HTML}{80425F}

% Complementary, Contrasting, and Harmonious Color Suggestions
% light_blue (#328998)
\definecolor{complement_light_blue}{HTML}{FFA500} % Complementary: Orange
\definecolor{contrast_light_blue}{HTML}{FF6F61}   % Contrasting: Coral
\definecolor{harmonious_light_blue}{HTML}{FFB6C1} % Harmonious: Light Pink

% light_gray (#434E5E)
\definecolor{complement_light_gray}{HTML}{FFFF99} % Complementary: Pale Yellow
\definecolor{contrast_light_gray}{HTML}{FFA500}   % Contrasting: Bright Orange
\definecolor{harmonious_light_gray}{HTML}{E6E6FA} % Harmonious: Light Lavender

% dark_blue (#3582C4)
\definecolor{complement_dark_blue}{HTML}{FFFF00} % Complementary: Yellow
\definecolor{contrast_dark_blue}{HTML}{FF0000}   % Contrasting: Red
\definecolor{harmonious_dark_blue}{HTML}{D3D3D3} % Harmonious: Light Gray

% green (#22A162)
\definecolor{complement_green}{HTML}{FF00FF} % Complementary: Magenta
\definecolor{contrast_green}{HTML}{FF0000}   % Contrasting: Red
\definecolor{harmonious_green}{HTML}{CCFFCC} % Harmonious: Light Yellow-Green

% purple (#59578E)
\definecolor{complement_purple}{HTML}{FFFF00} % Complementary: Yellow
\definecolor{contrast_purple}{HTML}{00FF00}   % Contrasting: Green
\definecolor{harmonious_purple}{HTML}{E6E6FA} % Harmonious: Lavender

% pink (#80425F)
\definecolor{complement_pink}{HTML}{008000} % Complementary: Green
\definecolor{contrast_pink}{HTML}{008080}   % Contrasting: Dark Teal
\definecolor{harmonious_pink}{HTML}{FFDAB9} % Harmonious: Peach

% Choose one of the colors as the main color
\colorlet{main_color}{light_blue} % Change this to the desired color
\colorlet{secondary_color}{contrast_pink} % Change this to the desired color
\input{glyphtounicode}


%---------- FONT OPTIONS ----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\color{main_color}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubItem}[1]{%
  \item\small{%
    #1 \vspace{-2pt}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textcolor{secondary_color}{\textbf{#1}} & \textcolor{secondary_color}{#2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeResearchheading}[2]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textcolor{secondary_color}{\textbf{#1}} & \textcolor{secondary_color}{\small#2}
    \end{tabular*}\vspace{-10pt}
}

\newcommand{\resumePaperheading}[2]{
  \vspace{-10pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1}  \\
      \quad \footnotesize#2
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeClassheading}[2]{
  \vspace{-10pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \footnotesize#2
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeEducationHeading}[6]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
      \textit{\small#5} & \textit{\small #6} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeProjectHeading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textcolor{secondary_color}{\textbf{#1}} & \textcolor{secondary_color}{\textit{\small #2}} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeOrganizationHeading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{\small #2} \\
      \textit{\small#3}
    \end{tabular*}\vspace{-7pt}
}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%---------- HEADING ----------

\begin{center}
    \textbf{\Huge \scshape \textcolor{main_color}{Jamshed Ashurov}} \\ \vspace{3pt}
    \small
    \faMobile \hspace{.5pt} \href{tel:15713158339}{+1 571 315 8339}
    $|$
    \faAt \hspace{.5pt} \href{mailto:jamshed00ashurov@gmail.com}{jamshed00ashurov@gmail.com}
    $|$
    \faGlobe \hspace{.5pt} \href{https://ashurja.github.io/}{\textcolor{secondary_color}{Portfolio}}
    $|$
    \faLinkedinSquare \hspace{.5pt} \href{https://www.linkedin.com/in/jamshed-ashurov/}{\textcolor{secondary_color}{LinkedIn}}
    $|$
    \faGithub \hspace{.5pt} \href{https://github.com/ashurja}{\textcolor{secondary_color}{GitHub}}
    % $|$
    % \faMapMarker \hspace{.5pt} \href{https://www.google.com/maps/place/Bogazici+University+North+Campus/@41.0863067,29.0441352,15z/data=!4m5!3m4!1s0x0:0x9d2497b07c8edb2f!8m2!3d41.0863067!4d29.0441352}{Istanbul, Turkey}
\end{center}



%----------- EDUCATION -----------

\section{Education}
  \vspace{3pt}
  \resumeSubHeadingListStart
    
    \resumeSubheading
      {UC San Diego}{La Jolla, California, USA}
      {BS in Computer Engineering}{Sep 2018 \textbf{--} June 2022}

    \resumeSubheading
      {UC San Diego}{La Jolla, California, USA}
      {MS in Computer Engineering/Machine Learning \& Data Science}{Sep 2022 \textbf{--} June 2024 (Expected)}

    % \resumeSubheading
    %   {Sandy Spring Friends School}{Sandy Spring, Maryland, USA}
    %   {High School Diploma}{July 2016 \textbf{--} Jun 2018}
    
  \resumeSubHeadingListEnd

%----------- WORK EXPERIENCE -----------

\section{Industry Experience}
  \vspace{3pt}
  \resumeSubHeadingListStart
    
    \resumeSubheading
      {Ampere Computing}{Portland, Oregon, USA}
      {CPU Architect Intern}{June 2023 \textbf{--} Sep 2023}
        \resumeItemListStart
            \resumeItem{Collaborated closely with the Architecture and Design team to assess the Architectural Vulnerability Factor(AVF) of various microprocessor structures using advanced emulation techniques via Cadence Palladium.}
            \resumeItem{Engineered and implemented an automated solution, streamlining the evaluation process and creating an adaptable infrastructure for potential integration with forthcoming chip designs.}
            \resumeItem{Collaborated with the Memory Controller Team to apply machine learning methods for memory controller performance optimization.}
            \resumeItem{Led the establishment of an experimental framework and selection of suitable machine learning models for single-performance metric optimization and multi-objective optimization problems.}
            % \resumeItem{Collaborated with the Firmware team, contributing to the development of a database-driven failure data collection tool.}
            % \resumeItem{Enhanced user experience by designing and refining the graphical user interface (GUI) of the data collection tool, subsequently ensuring its smooth deployment across existing devices.}
        \resumeItemListEnd
    
    \resumeSubheading
      {Nanome Inc.}{San Diego, California, USA}
      {Software Engineering Intern}{Jun 2019 \textbf{--} Sep 2019}
        \resumeItemListStart
            \resumeItem{Developed AR application utilizing C\# on iOS devices, to aid in analyzing 3D protein structures without the requirement of a VR setup.}
            \resumeItem{Architected a robust local database system, integrating it into the application's framework to efficiently store and manage data elements retrieved from an online database source.}
            \resumeItem{Implemented preliminary scripts, fostering cross-platform versatility and laying the foundation for the application's potential expansion to other platforms.}
        \resumeItemListEnd
    
  \resumeSubHeadingListEnd



%----------- RESEARCH EXPERIENCE -----------

\section{Research \& Teaching Experience}
  \vspace{3pt}
  \resumeSubHeadingListStart
  
    \resumeResearchheading{UC San Diego Research Assistant}{Jan 2022 - Sep 2023}
      \resumePaperheading{Characterizing WebAssembly Performance in the Era of Serverless Computing}{\textbf{Jamshed Ashurov}, Zixuan Wang, Jishen Zhao}
      \resumeItemListStart
            % \resumeItem{Developed microbenchmarks to analyze the performance of WebAssembly System Interface(WASI) at a fine granularity.}
            % \resumeItem{Wrote scripts to analyze the performance of WASI on various architectures using Linux profiling tools.}
            % \resumeItem{Instrumenting the WebAssembly runtime to collect performance metrics.}
            \resumeItem{\href{https://conf.researchr.org/details/ecoop-issta-2023/ecoop-issta-2023-student-research-competition/7/-Characterizing-WebAssembly-Performance-in-the-Era-of-Serverless-Computing}{\textcolor{secondary_color}{\textit{\underline{ISSTA 2023 SRC}}}}}
      \resumeItemListEnd

      \resumeResearchheading{UC San Diego Graduate Teaching Assistant}{Jan 2023 \textbf{--} Present}
      \resumeClassheading{Computer Networks}{Aaron Schulman, Alex Snoeren}
        \resumeItemListStart
            \resumeItem{Designed and developed the source code and the testing framework for students to implement Sliding Window Protocol and TCP Congestion Control mechanisms.}
            \resumeItem{Assisted students with understanding/debugging in building a simple router.}
        \resumeItemListEnd

  \resumeSubHeadingListEnd
  %----------- TEACHING EXPERIENCE -----------

  % \section{Teaching Experience}
  % \vspace{3pt}
  % \resumeSubHeadingListStart

    
  % \resumeSubHeadingListEnd

%----------- PROJECTS -----------

\section{Projects}
    \vspace{3pt}
    \resumeSubHeadingListStart

      \resumeProjectHeading
      {\textbf{Statistical Inference and Machine Learning}}{MATLAB}
      % $|$ \emph{\href{https://github.com/arasgungore/CMPE250-projects}{\color{blue}GitHub}}}{}
      \resumeItemListStart
        \resumeItem{Possess deep knowledge of the theory and direct, library-free implementation of Bayesian Decision Theory, Maximum Likelihood Estimation, Bayesian Parameter Estimation, Expectation-Maximization (EM), Principal Component Analysis(PCA), Linear Discriminant Analysis(LDA), and optimization methods such as Gradient Descent, Newton Descent, Simulated Annealing, Cross Entropy Minimization, and Search Gradient.}
        \resumeItem{Applied these concepts to solve an image processing problem of teaching a computer to segment an image into background and foreground with an error rate of less than 5\%.}
      \resumeItemListEnd

      \resumeProjectHeading
      {\textbf{Web Mining and Recommender Systems}}{Python, TensorFlow, Keras}
      % $|$ \emph{\href{https://github.com/arasgungore/CMPE250-projects}{\color{blue}GitHub}}}{}
        \resumeItemListStart
          \resumeItem{Developed and implemented a Latent Factor Model(LFM) using TensorFlow's Keras API to predict ratings based on user interactions with recipes, reducing Mean Squared Error (MSE) from 1.708 (baseline) to 1.489.}
          \resumeItem{Developed and implemented a Bayesian Personalized Ranking(BPR) model to predict user interactions with recipes, enhancing accuracy from 50\% (baseline) to 72\%.}
        \resumeItemListEnd

      \resumeProjectHeading
      {\textbf{Advanced Microprocessor Design}}{System Verilog, Verilator, Python, Bash}
      % $|$ \emph{\href{https://github.com/arasgungore/CMPE250-projects}{\color{blue}GitHub}}}{}
        \resumeItemListStart
          \resumeItem{Improved 5-stage pipelined MIPS 32 processor with advanced optimizations in System Verilog, achieving significant performance gains across all benchmarks. Utilized bash and Python scripts to analyze and collect performance data.}
          \resumeItem{Implemented 8KB 8-component TAGE branch predictor, reducing mispredictions by \(94.3\%(99.1\%)\) on average across all benchmarks compared to the baseline predictor.}
          \resumeItem{Developed a victim cache using NRU replacement policy, resulting in an average CPI reduction of 10.2\%(19.9\%) compared to the baseline across all benchmarks.}
          \resumeItem{Implemented DRRIP cache replacement policy, reducing dcache misses by \(31.4\%(80.3\%)\) compared to the baseline direct mapped cache across all benchmarks.}
          \resumeItem{Modified the baseline in-order pipeline to scalar OOO processor with Partial Ordering for memory disambiguation policy. Achieved an average CPI reduction of 8.9\%(13.15\%) across all benchmarks compared to the baseline.}
        \resumeItemListEnd

      \resumeProjectHeading
        {\textbf{Intellectual Robotic Chess Player Arm}}{Python, TensorFlow, Keras, ONNX, Raspberry Pi}
        % $|$ \emph{\href{https://github.com/arasgungore/rocket-flight-simulator}{\color{blue}GitHub}}}{}
          \resumeItemListStart
            \resumeItem{Utilized a range of convolutional neural network (CNN) models, including Xception, MobileNet, SqueezeNet, and NASNetMobile, to capture and process real-time images of the chessboard.}
            \resumeItem{Employed different runtimes, such as TensorFlow and ONNX, to optimize the detection process.}
            \resumeItem{Integrated an AI chess engine, Stockfish, to generate the next move and coordinated the Raspberry Pi to control the robotic arm and execute the determined move.}
          \resumeItemListEnd

      \resumeProjectHeading
        {\textbf{Parallel Computing}}{CUDA}
        % $|$ \emph{\href{https://github.com/arasgungore/netlist-solver}{\color{blue}GitHub}}}{}
          \resumeItemListStart
            \resumeItem{Developed and optimized CUDA-based convolutional layer for the LeNet-5 architecture, significantly improving inference performance while maintaining high accuracy.}
            \resumeItem{Converted 2D convolution operations into tiled matrix multiplications for better cache utilization to achieve faster execution time.}
          \resumeItemListEnd

      \resumeProjectHeading
        {\textbf{Snek Compiler}}{Rust, x86}
        % $|$ \emph{\href{https://github.com/arasgungore/filters-and-fractals}{\color{blue}GitHub}}}{}
          \resumeItemListStart
            \resumeItem{Developed a compiler for the dynamically typed language Snek in Rust, integrating the Mark and Compact garbage collection algorithm to efficiently manage memory and remove garbage data.}
            \resumeItem{Orchestrated the transition to Administrative Normal Form and subsequently to Intermediate Representation for effective code transformation and optimization.}
            \resumeItem{Introduced optimization techniques, including constant folding and variable propagation, to enhance the binary file size and improve program execution efficiency.}
          \resumeItemListEnd
      
      \resumeProjectHeading
        {\textbf{Dual Core Machine Learning Hardware Accelerator for Attention Mechanism}}{}
        % $|$ \emph{\href{https://github.com/arasgungore/chess-bot}{\color{blue}GitHub}}}{}
          \resumeItemListStart
            \resumeItem{Utilized RTL design, verification, logic synthesis, and place-and-route (PnR) methodologies to generate gate-level netlist and layout for a ML hardware accelerator via Synopsis Design Compiler (DC) and Cadence Innovus.}
            \resumeItem{Implemented advanced low-power techniques, including pipelining, loop unrolling, asynchronous FIFO, and clock gating, to optimize the power consumption of the design.}
          \resumeItemListEnd
      
      \resumeProjectHeading
        {\textbf{Fault Tolerant and Scalable Surfstore}}{Golang, gRPC, Python, Bash}
        % $|$ \emph{\href{https://github.com/arasgungore/netlist-solver}{\color{blue}GitHub}}}{}
          \resumeItemListStart
            \resumeItem{Developed a robust file-sharing application, closely resembling the functionalities of Dropbox.}
            \resumeItem{Implemented consistent hashing for even data distribution, minimal movement during node scaling, and fault tolerance for seamless operations across numerous nodes.}
            \resumeItem{Employed the RAFT consensus algorithm to establish leader election, log replication, and fault recovery mechanisms, ensuring high availability and data integrity within the distributed system.}
          \resumeItemListEnd

    \resumeSubHeadingListEnd


%----------- AWARDS & ACHIEVEMENTS -----------

% \section{Awards \& Achievements}
%   \vspace{2pt}
%   \resumeSubHeadingListStart
%     \small{\item{
%         \textbf{National University Admission Exam (YKS):}{ Ranked $75^{th}$ in Mathematics and Science among ca. 2.3 million candidates with a test score of 489.92/500.} \\ \vspace{3pt}
        
%         \textbf{KYK Outstanding Success Scholarship:}{ Awarded to undergraduate students who have been ranked in the top 100 on National University Admission Exam by Higher Education Credit and Hostels Institution (KYK).} \\ \vspace{3pt}
        
%         \textbf{Boğaziçi University Success Scholarship:}{ Awarded to undergraduate students who have been ranked in the top 100 on National University Admission Exam by Boğaziçi University.} \\ \vspace{3pt}
        
%         \textbf{TÜBİTAK 2247-C Intern Researcher Scholarship:}{ Awarded to undergraduate students who take part in research projects carried out by the Scientific and Technological Research Council of Turkey (TÜBİTAK).} \\ \vspace{3pt}
        
%         \textbf{Duolingo English Test (DET):}{ Overall Score: 135/160} \\ \vspace{3pt}
        
%         % \textbf{Boğaziçi University English Proficiency Test (BUEPT):}{ Achieved the highest grade A on the BUEPT grading scheme with a total score in the range of 85-100.} \\ \vspace{3pt}
        
%         \textbf{Kocaeli Science High School Salutatorian Award:}{ Graduated as the second-highest ranked student in my class.}
%     }}
%   \resumeSubHeadingListEnd



%----------- SKILLS -----------

\section{Skills}
  \vspace{2pt}
  \resumeSubHeadingListStart
    \small{\item{
        \textcolor{secondary_color}{\textbf{Programming:}}{ C, Python, System Verilog, C++, Rust, Golang, MATLAB, Java, C\#, Shell, Tcl, CUDA, Haskell, x86/ARM/MIPS Assembly.} \\ \vspace{3pt}
        
        \textcolor{secondary_color}{\textbf{Tools:}}{ Cadence Palladium/Virtuoso/Innovus, Synopsis Verdi/Design Compiler, ModelSim, Quartus, Questa, Verilator, Unity3D, Fusion360.} \\ \vspace{3pt}

        \textcolor{secondary_color}{\textbf{Technical Skills:}}{ Microprocessor Design, Machine Learning, Compiler Design, Parallel Computing, Logic Design, Performance Profiling, Software Development, Reliable and Scalable System Development, Universal Verification Method(UVM), Analog Circuit Analysis.} \\ \vspace{3pt}
        
        \textcolor{secondary_color}{\textbf{Soft Skills:}}{ Leadership, Teamwork, Public Speaking, Coaching, Teaching.} \\ \vspace{3pt}
        
        \textcolor{secondary_color}{\textbf{Additional Skills:}}{ Ballroom and Latin Dancing, Martial Arts, Rock Climbing.} \\ \vspace{3pt}

        \textcolor{secondary_color}{\textbf{Languages:}}{ Tajik (Native), Russian (Native), English (Professional).}
        
        % \textbf{Frameworks}{: X, X, X} \\
        % \textbf{Developer Tools}{: X, X, X} \\
        % \textbf{Libraries}{: X, X, X} \\
        % \textbf{Applications}{: X, X, X}
    }}
  \resumeSubHeadingListEnd



%----------- RELEVANT COURSEWORK -----------

% \section{Relevant Coursework}
%   \vspace{2pt}
%   \resumeSubHeadingListStart
%     \small{\item{
%         \textbf{Major coursework:}{ Calculus I-II, Matrix Theory, Differential Equations, Materials Science, Electrical Circuits I-II, Digital System Design, Numerical Methods, Probability Theory, Electronics I-II, Signals and Systems, Electromagnetic Field Theory, Energy Conversion, System Dynamics and Control, Communication Engineering} \\ \vspace{3pt}
        
%         \textbf{Minor coursework:}{ Discrete Computational Structures, Introduction to Object-Oriented Programming, Data Structures and Algorithms}
%     }}
%   \resumeSubHeadingListEnd



%----------- CERTIFICATES -----------

% \section{Certificates}
  % \resumeSubHeadingListStart
    
    % \resumeOrganizationHeading
      % {Procter \& Gamble VIA Certificate Program}{Feb 2022}{Business Skills, Data and Digital Skills, Project Management and Personal Productivity}
    
  % \resumeSubHeadingListEnd



%----------- ORGANIZATIONS -----------

% \section{Organizations}
  % \resumeSubHeadingListStart
    
    % \resumeOrganizationHeading
      % {Institute of Electrical and Electronics Engineers (IEEE)}{Feb 2022 -- Present}{Student Member}
    
  % \resumeSubHeadingListEnd



%----------- HOBBIES -----------

% \section{Hobbies}
  % \resumeSubHeadingListStart
    % \small{\item{Swimming, Fitness, Eight-ball}}
  % \resumeSubHeadingListEnd



%----------- REFERENCES -----------

% \section{References}
  % \resumeSubHeadingListStart
    
  % \resumeSubHeadingListEnd



%-------------------------------------------
\end{document}
